Structural controllability of ecological networks

### 2018-06-28 paper/manuscript.Rmd
Oops missed some references

The median size of the relative minimum driver-node set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
This value is high when compared to other complex systems in which controllability has been investigated;  
for instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011]. 
These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@addrefs].

@@

Structural controllability assumes that the networks can be approximated using linear functional responses [@addrefs]. 
The ramifications of this assumption imply that, while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the *exact* interventions that should be applied to these species in order to achieve a desired state. 
In an ideal scenario, we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios. 
\R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species. 
By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
<!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
<!-- Made some edits, we'll se what people say -->

>>>>

The median size of the relative minimum driver-node set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
This value is high when compared to other complex systems in which controllability has been investigated;  
for instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011]. 
These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@woodford_confronting_2016].

@@

Structural controllability assumes that the networks can be approximated using linear functional responses [@liu_control_2016]. 
The ramifications of this assumption imply that, while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the *exact* interventions that should be applied to these species in order to achieve a desired state. 
In an ideal scenario, we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios. 
\R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species. 
By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
<!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
<!-- Made some edits, we'll se what people say -->
